The Impact of Interview Disruptions on Data Quality in Social Surveys

### 2024-11-26 paper/paper.qmd
update paper of validation and model details

## Implications for Managing Interview Interference**

@@

## Limitations and Areas for Improvement**

@@

## Future Research Directions**

@@

## Practical Insights for Survey Management**

@@

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

@@

```
## Validation
```{r}

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")
vif(first_model)

>>>>

## Implications for Managing Interview Interference

@@

## Limitations and Areas for Improvement

@@

## Future Research Directions

@@

## Practical Insights for Survey Management

@@

## Posterior predictive check
###Validation
```{r}
#| echo: false
#| warning: false

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")+ xlim(-0.1, 1.2)

vif(first_model)

@@
